Fast matrix transpose on Parallel Architectures\\

### 2024-10-23 latex/paper.tex
first_assignment: sequencial matTranspose

\documentclass[12pt]{article}

\usepackage{sectsty}    % set section font
\usepackage{graphicx}
\usepackage{blindtext}  % generate random text
\usepackage{multicol}   % multiple columns
\usepackage[a4paper,
            bindingoffset=.2in,
            left=.45in,
            right=.65in,
            top=.8in,
            bottom=1in,
            footskip=.5in]  % page number
            {geometry}

% set font family
\usepackage{times}
\usepackage{anyfontsize}

% set roman numbers in sections
\renewcommand{\thesection}{\small\Roman{section}}
% set section and subsection font
\sectionfont{\fontsize{9}{1}\selectfont\sffamily}
\subsectionfont{\fontsize{9}{1}\selectfont\itshape}

% TODO:
% - change the title font
% - change the section font, center, roman numbers

% begin ---------------------------------------
\begin{document}

\fontsize{9}{10}\selectfont  % set font size and spacing

\begin{center}
\section*{\huge{\sffamily The potential of high-performance computing
for the Internet of Sounds}}
Giovanni Santini \\
\textit{Dept.\ of Information Engineering \\
and Computer Science} \\
\textit{University of Trento} \\
Tento, Italy \\
giovanni.santini@unitn.it
\end{center}

\bigskip

\begin{multicols}{2}

\textbf{\textit{Abstract}--
High-Performance Computing (HPC) technology is
impacting several industries, including the creative industries
and those operating in the Internet of Things. However, thus
far, scarce attention has been devoted by researchers to the use
of such technology in Internet of Sounds (IoS) settings. The
IoS is a new area emerging in industry and academia as an
extension of the IoT to the sonic domain, both in musical and
non-musical contexts. The IoS relates to a distributed network
of sound things, which are devices capable of sensing, acquiring,
processing, actuating, and exchanging data serving the purpose
of communicating sound-related information. In this position
paper, we investigate the integration of HPC technology with
the IoS. We illustrate such integration via a set of application
scenarios showing how the IoS can benefit from HPC.\ Finally, we
discuss the open challenges ahead of us to implement a successful
integration of these two kinds of technology. \\
\indent \textit{Index Terms}--Internet of Sounds, High-Performance
Computing, audio processing
}

\fontsize{9}{11}\selectfont  % set font size and spacing

\begingroup\centering\section{INTRODUCTION}\endgroup

% lorem ipsum
\blindtext\blindtext\blindtext

\begingroup\centering\section{RELATED WORK}\endgroup

\blindtext\blindtext\blindtext

\begingroup\centering\section{BODY}\endgroup

\blindtext\blindtext\blindtext

\begingroup\centering\section{EVALUATION}\endgroup

\blindtext\blindtext\blindtext

\begingroup\centering\section{CONCLUSIONS}\endgroup

\blindtext\blindtext\blindtext

\begingroup\centering\section{APPENDIX}\endgroup

\blindtext\blindtext\blindtext

\begingroup\centering\section{ACKNOWLEDGMENTS}\endgroup

\blindtext\blindtext\blindtext

% end -----------------------------------------
\end{multicols}
\end{document}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{blindtext}  % generate random text
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Fast matrix transpose on Parallel Architectures\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Giovanni Santini}
\IEEEauthorblockA{\textit{Dept.\ of Information Engineering and Computer Science} \\
\textit{University of Trento}\\
Trento, Italy \\
giovanni.santini@unitn.it \\
MAT. 235441}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}

Introduction of the problem and importance. \\
- Describe the background and importance of the problem \\
- Outline the main objectives of your project \\

\blindtext\blindtext

\section{State of the Art}

- Review current research and developments related to your project \\
- Discuss existing solutions and their limitations \\
- Identift the gap your project aims to fill \\

\blindtext\blindtext

\section{Contribution and Methodology}

- Elaborate on the unique contributions of your project \\
- Describe the methodology proposed, including algorithms (pseudo-code),
data structures, and parallelization techniques. \\
- Discuss the challenges faced and how they were addressed \\

\blindtext\blindtext

\section{Experiments and System Description}

- Detailed description of the computing system and platform. \\
- Relevant specifications or configurations (e.g., libraries
and programming toolchains). \\
- Description of the experimental setup, procedures, and
methodologies used in the project. \\
- Discussion on how experiments are designed to test the hypotheses
or achieve the objectives \\

\blindtext\blindtext

\section{Results and Discussion}

- Presentation of results \\
- Analysis and interpretation in context \\
- Comparison with the state-of-the-art \\

\blindtext\blindtext

\section{Conclusions}

- Summary of the key findings and contributions

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}

\end{document}
